---
title: "Characterizing Automobiles"
author: "Your Name Here"
date: "03/17/2025"

format: 
  html:  # You will quite likely want to change all but the last one, to taste
    theme:
        light: flatly
        dark: darkly
    mainfont: monospace
    highlight-style: github
    title-block-banner: true
    embed-resources: true

---

# Setup

- Setup

```{r libs}
sh <- suppressPackageStartupMessages
sh(library(tidyverse))
sh(library(caret))
sh(library(fastDummies))
sh(library(class))
sh(library(ISLR)) # for the "Auto" dataframe
```

# Dataframe

- We use the `Auto` dataframe.

```{r df}
head(Auto)
```

- It has the following variable names, which describe various attributes of automobiles.

```{r df2}
names(Auto)
```

# Multiple Regression

- Run a linear regression model with `mpg` as the dependent variable and `horsepower` and `year` as features (variables).
- Compute and comment on the RMSE.

```{r regression}
# Your code here
```

> <span style="color:red;font-weight:bold">TODO</span>: *Explain*

# Feature Engineering

- Create 10 features based on the `name` column.
- Remove all rows with a missing value.
- Ensure only `mpg` and the engineered features remain.
- Compute and comment on the RMSE.

```{r features}
# Your code here
```

> <span style="color:red;font-weight:bold">TODO</span>: *Explain*

# Classification

- Use either of $K$-NN or Naive Bayes to predict whether an automobile is a `chevrolet` or a `honda`.
- Explain your choice of technique.
- Report on your Kappa value.

```{r classification}
# Your code here
```

> <span style="color:red;font-weight:bold">TODO</span>: *Explain*

# Binary Classification

- Predict whether a car is a `honda`.
- Use model weights.
- Display and comment on an ROC curve.

```{r binary classification}
# Your code here
```

> <span style="color:red;font-weight:bold">TODO</span>: *Explain*

# Ethics

- Based on your analysis, comment on the [Clean Air Act of 1970 and Ammendments of 1977](https://www.epa.gov/clean-air-act-overview/evolution-clean-air-act)
- Discuss the civic reposibilities of data scientists for:
    - Big Data and Human-Centered Computing
    - Democratic Institutions
    - Climate Change
- Provide at least one statistical measure for each, such as a RMSE, Kappa value, or ROC curve.

> <span style="color:red;font-weight:bold">TODO</span>: Big Data and Human-Centered Computing

```{r big data}
# Your code here
```

> <span style="color:red;font-weight:bold">TODO</span>: Democratic Institutions

```{r democracy}
# Your code here
```

> <span style="color:red;font-weight:bold">TODO</span>: Climate Change

```{r climate}
# Your code here
```